---
title: "midterm_practice"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.



、、、{r}
Sys.setenv(LANG = "en")

＃R has six basic ('atomic') vector types: logical, integer, real, complex, string (or character) and raw.

、、、{r}
c("John", "Mary")
list("John", 178, TRUE)
list("John", 5, TRUE) # has 3 element values.


、、、{r}
list("John",42, list("Mary", 35)) 
## Within a vector, each element value is not sitting inside another vector.Therefore, the above vector has the following three element values: 
"John"
42
list("Mary", 35)You CANNOT say "Mary" is an element value of the big list, since it sits inside another vector.##

##We can retrieve a value from the vector using [[]]

#Exercise2.1 list("John",42, list("Mary", 35)) 
list("John",42, list("Mary", 35))[[2]]
#[[x]] can be followed immediately by another [[y]]
list("John",42, list("Mary", 35))[[3]][[1]]

、、、{r}
#binding
c(2, 3.1415) -> interestingnumber
personName <- c("John", "Mary")
interestingnumber[[2]]
interestingNumber = c(2, 3.1412)

##regular name starts with small case.
##regular valid name starts with a letter or the dot not followed by a number.



#EX5
```{r}
concerts_obo -> concerts_oboCopy
# add one more show, and
# shares the same show information as its first show
# name call to retrieve a non-existent element value: concerts_oboCopy[[5]]$showInfo[[2]]
# give that name call retrieval the value you want use binding <- 
concerts_oboCopy[[5]]$showInfo[[2]] <- 
  concerts_oboCopy[[5]]$showInfo[[1]]
# except the date is 2 days later
#  modify new show's day information
# check wrong values to be corrected
concerts_oboCopy[[5]]$showInfo[[2]]$time 
concerts_oboCopy[[5]]$showInfo[[2]]$endTime  
# correct the values
concerts_oboCopy[[5]]$showInfo[[2]]$time <-
  "2022/05/16 10:00:00" 
concerts_oboCopy[[5]]$showInfo[[2]]$endTime <-
  "2022/05/17 22:00:00"
concerts_oboCopy[[5]]$showInfo[[2]] # name call to show answer



##Concatenate
c(list("a", 1), list("c", 2)) chains all values together as list("a", 1, "c", 2) 
but! list(c("a", "b"), c("c", "d")) does not same as list("a", "b", "c", "d")



、、、{r}
coercion <- c(c("a", "b"), c(1, 22))


、、、{r}
list(
  c(54, 32, 28, 20), # age
  c("male", "female", "female", "male"), # gender
  c("north", "south", "east", "east"), # residence
  c(100, 25, NA, 77) # income  
)


##In a vector, we can give each element value a name, using "name"=value

c("John"=177, "Mary"=160, "Bill"=170)   # atomic vector

list("John"=177, "Mary"=160, "Bill"=170)   # list

、、、{r}
list(
  "1st Observation"=list(54, "male", "north", 100), 
  "2nd Observation"=list(32, "female", "south", 25), 
  "3rd Observation"=list(28, "female", "east", NA), 
  "4th Observation"=list(20, "male", "east", 77), 
)

list(
  firstObservation=list(54, "male", "north", 100), 
  secondObservation=list(32, "female", "south", 25))
  
##<- or -> is merely for binding purpose.


sample_data <- 
  list(
    "1st Observation"=list(54, "male", "north", 100), 
    "2nd Observation"=list(32, "female", "south", 25)
  )
sample_data[["2th Observation"]]

##[[裡面可以放位置或“Name”]]

##Other than [["value_name"]] you can also use $"value_name" or $``value_name``, or when value_name is regular, $value_name

sample_data <- list(
  "observation1"=list(54, "male", "north", 100), 
  "observation2"=list(32, "female", "south", 25),
)
sample_data[["observation4"]]
sample_data$"observation4"
sample_data$`observation4`
sample_data$observation4


##There are two types of list :1.non-labelled items 2.Labelled items

list(
  list(
    name="name1",
    time="time1",
    program=list(
      "music1",
      "music2"
    )
  ),
  list(
    name="name2",
    time="time2",
    program=list(
      "musicA",
      "musicB"
    )
  )
)



list(
  course1 = list(
    name = "Program For Data Science",
    time = "Wed. Session 5-6",
    place = "IT-B1F-06"
  ),
  course2 = list(
    name = "Economics",
    time = "Wed. Session 3-4",
    place = "S-105"
  )
)


## Observation by observation
concerts_obo <-
  jsonlite::fromJSON("https://cloud.culture.tw/frontsite/trans/SearchShowAction.do?method=doFindTypeJ&category=17", simplifyDataFrame = F)

## Feature by feature
concerts_fbf <-
  jsonlite::fromJSON("https://cloud.culture.tw/frontsite/trans/SearchShowAction.do?method=doFindTypeJ&category=17", simplifyDataFrame = T)
  
  
##fromJSON can take both an URL or a file path of a .json file
##simplifyDataFrame controls importing a json data source observation-by-observation (F) or feature-by-feature (T).
Feature by feature data set is called a data frame.


# checking how many element values
length(JohnsFamily)
# checking element names
names(JohnsFamily)


#Sys.Date() # show the date today


JohnsFamily <-
     list(
         name = "John", 
         age = 35,
         spouse = list(
             name = "Mary", 
             age = 32),
         children = list(
             list(
                 name = "Bill", 
                 age = 5),
             list(
                 name = "Jane", 
                 age = 3)
         )
     )
     
##retreive
[ ] is designed to retrieve multiple element values. Its resulting vector will always follow the same type as the source object.

、、、{r}
JohnsFamily[c(1,2)]
JohnsFamily[c("name", "age")]
     
##replacement    
JohnsFamilyCopy <- JohnsFamily
JohnsFamilyCopy[[1]] <- "Watson" 

JohnsFamilyCopy[c(1,2)] <- 
  list(name="Watson", age=37) 
JohnsFamilyCopy[c(1,2)]


##add value 
[ ] <- has to bind a value that is consistent with source object type. example1[c(7, 8)] is a character atomic vector, so example1[c(7, 8)] <- can only bind with a character atomic vector.


### declare a numeric object
object_numeric <- numeric(0)

# declare a character object
object_character <- character(0)

# declare a logical object 
object_logical <- logical(0)

#**Be aware! To declare an empty list object:
object_list <- list()



##
classSchedule <- list()  #declare
> classSchedule$yr108$semester1[[1]] <- course1 #add value
> classSchedule #call name
$yr108
$yr108$semester1
$yr108$semester1[[1]]
$yr108$semester1[[1]]$name
[1] "programming for data science"

$yr108$semester1[[1]]$credit
[1] 2
